Thesis Title

### 2022-04-04 chapters/chapter_2.tex
add introduction to chap 4

As mentioned in Chapter \ref{sssec:shotgun_metagenomics}, \ac{SMg} approaches have been a growing interest to deliver clinically relevant results without \textit{a priori} knowledge of what to expect from a particular clinical sample or patient. 
The capacity to detect all potential pathogens in a sample has great potential utility in the diagnosis of infectious disease. 
However, it is unclear how the variety of available methods impacts the end results.

>>>>

As mentioned in Chapter \ref{ch:introduction}, section \ref{sssec:_intro_shotgun_metagenomics}, \ac{SMg} approaches have been a growing interest to deliver clinically relevant results without \textit{a priori} knowledge of what to expect from a particular clinical sample or patient. 
The capacity to detect all potential pathogens in a sample has great potential utility in the diagnosis of infectious disease. 
However, it is unclear how the variety of available methods impacts the end results.

### 2022-04-04 chapters/chapter_3.tex
add introduction to chap 4

As referenced in section \ref{ssec:survaillance}, sequencing has become a common tool in surveillance and infection prevention, when combined with epidemiological data, have undoubtedly provided immeasurable insights regarding identification of potential sources of pathogenicity and transmission pathways. Shotgun metagenomic (SMg) approaches, just like in a clinical setting,  have been a growing interest to deliver relevant results without a priori knowledge of what to expect from a particular environmental sample.

In this publication, second (see \ref{ssec:2nd_gen_seq}) and third (see \ref{ssec:3rd_gen_seq}) generation sequencing SMg has been applied to eight concentrated water samples collected the University Medical Center Groningen. In one of the samples, the novel detection of an \textit{mcr-5} gene, named \textit{mcr-5.4}, is reported. To the best of our knowledge, this is the first time that this gene, a mobile colistin resistance (\textit{mcr}) determinant, has been recovered from a hospital water environment, with analysis suggesting the order of \textit{Pseudomonadales} as the most probable host.

>>>>

As referenced in Chapter \ref{ch:introduction}, section \ref{ssec:_intro_survaillance}, sequencing has become a common tool in surveillance and infection prevention, when combined with epidemiological data, have undoubtedly provided immeasurable insights regarding identification of potential sources of pathogenicity and transmission pathways. Shotgun metagenomic (SMg) approaches, just like in a clinical setting,  have been a growing interest to deliver relevant results without a priori knowledge of what to expect from a particular environmental sample.

In this publication, second (see Chapter \ref{ch:introduction}, section \ref{ssec:_intro_2nd_gen_seq}) and third (see Chapter \ref{ch:introduction}, section \ref{ssec:_intro_3rd_gen_seq}) generation sequencing SMg has been applied to eight concentrated water samples collected the University Medical Center Groningen. In one of the samples, the novel detection of an \textit{mcr-5} gene, named \textit{mcr-5.4}, is reported. To the best of our knowledge, this is the first time that this gene, a mobile colistin resistance (\textit{mcr}) determinant, has been recovered from a hospital water environment, with analysis suggesting the order of \textit{Pseudomonadales} as the most probable host.

### 2022-04-04 chapters/chapter_4.tex
add introduction to chap 4

LA LA LA

@@

\ac{CDS}; \ac{DENV}; \ac{HPC}; \ac{HTS}; NCR, non-coding region; QC, quality control; RT-PCT, reverse transcription polymerase chain reaction.

>>>>

\ac{DENV} represents a public health threat and economic burden in affected countries. The risk of exposure to \ac{DENV} is increasing, not only because of travel to endemic regions, but also due to the broader dissemination of the mosquito vector, making the burden of dengue very significant.

The availability of genomic data is key to understanding viral evolution and dynamics, supporting improved control strategies. Currently, the use of second-generation sequencing technologies, which can be applied both directly to patient samples (shotgun metagenomics) and to PCR-amplified viral sequences (amplicon sequencing), is the most informative approach to monitor viral dissemination and genetic diversity by providing, in a single methodological step, identification and characterization of the whole viral genome at the nucleotide level. This makes \ac{DENV} identification and characterization through genomic analysis by developing a software where the lessons learned in Chapters \ref{ch:paper1} and \ref{ch:paper2} are applied.

We have developed DEN-IM, a one-stop, user-friendly, containerised and reproducible workflow for the analysis of Dengue virus short-read sequencing data from both amplicon and shotgun metagenomics approaches. EN-IM was designed to perform a comprehensive analysis in order to generate either assemblies or consensus of full DENV coding sequences and to identify their serotype and genotype. DEN-IM can also detect all four DENV serotypes and the respective genotypes present in a spiked sample, raising the possibility that DEN-IM can play a role in the identification of co-infection cases whose prevalence is increasingly perceived in highly endemic areas.

My contribution to this publication included the design, implementation and optimisation of the DEN-IM the workflow, including the creation of  the Docker containers for all dependencies. Two databases, one comprising 3830 \ac{DENV} sequences for the retrieval of the reads of interest from the input samples, and a second comprising of 161 sequences representing the genetic diversity of all \ac{DENV} sero and genotypes were constructed by me.  Additionally, I've also wrote the manuscript.

@@

\ac{CDS}; 
Dengue virus ( \ac{DENV}); 
\ac{HPC}; 
\ac{HTS}; 
\ac{NCR}; 
\ac{QC}; 
Reverse Transcription Polymerase Chain Reaction (RT\_PCR)
